\subsection{Testing Batch Transactions}
\subsubsection{BANK-APP}
\begin{longtable}[l]{ p{2.3cm} | p{.79\linewidth} }\hline
    & \textbf{BANK-APP} \\ \hline
    \textbf{Observation} & It was found that the Batch transactions feature does not work as expected. Irrespective of the number of transaction entries provided in the batch file, only the last transaction is always performed. \\
    \textbf{Discovery} &
        This vulnerability was discovered in \enquote{New Transaction} page. Steps are as follows:
             \begin{itemize}
              \item Login as a customer and go to the \enquote{New Transaction} page. Upload a file with multiple valid transaction entries.

              \item After clicking on Submit, a success message is displayed. Go to the \enquote{Transactions} page and note that only the last transaction is displayed.
             \end{itemize} \\
    \textbf{Likelihood} & N/A\\
    \textbf{Impact} & It is not possible for the user to perform batch transactions. The file upload feature, hence becomes equivalent to using the HTML form, for making transfers. \\
    \textbf{Recommen\-dations} & It is recommendable that the feature is implemented in entirety. \\ \hline
    \textbf{CVSS} & N/A
    \\ \hline
\end{longtable}

\subsubsection{SecureBank}
\begin{longtable}[l]{ p{2.3cm} | p{.79\linewidth} }\hline
    & \textbf{SecureBank} \\ \hline
    \textbf{Observation} & It was found that batch upload feature works as expected, and performs multiple transactions successfully. \\
    \textbf{Discovery} & The same steps were performed and found that all the transactions provided in the uploaded file were displayed in the Transaction history. \\
    \textbf{Likelihood} & N/A \\
    \textbf{Impact} & N/A \\
    \textbf{Recommen\-dations} & N/A \\ \hline
    \textbf{CVSS} & N/A
    \\ \hline
\end{longtable}

\subsubsection{Comparison}
SecureBank has a functioning implementation of the batch-upload feature compared to BANK-APP where the feature, though exists does not serve its purpose completely.
\clearpage