\subsection{Analysis of Stack Traces - OTG-ERR-002}
\subsubsection{BANK-APP}
\begin{longtable}{ p{2.3cm} | p{.79\linewidth} }\hline
    & \textbf{BANK-APP} \\ \hline
    \textbf{Observation} & 
    	We could not detect stack traces in this application.
    \\
    \textbf{Discovery} &
    	See OTG-ERR-001.
    \\
    \textbf{Likelihood} &
    	N/A
    \\
    \textbf{Impact} & 
    	N/A
    \\
    \textbf{Recommen\-dations} &
        N/A
    \\ \hline
    \textbf{CVSS} &
        N/A
    \\ \hline
\end{longtable}

\subsubsection{SecureBank}
\begin{longtable}{ p{2.3cm} | p{.79\linewidth} }\hline
    & \textbf{SecureBank}
    \hfill CVSS Score: 0 \progressbar{0}
    \\ \hline
    \textbf{Observation} & 
    	The Application outputs a php exception with stack trace if a page is accessed unauthorized. See~\ref{fig:OTG_ERR_001_3}. \newline
        The Stack Trace suggests the application contains at least the following parts:
        \begin{itemize}
          \item \textbf{MVC pattern:} \enquote{EmployeeController.php} 
          \item \textbf{Routing component:} \enquote{RoutingService.php} 
          \item \textbf{Authentification component:} \enquote{RoutingService.php} 
          \item \textbf{Request abstraction:} \enquote{Helper\textbackslash Request} 
        \end{itemize}
    \\
    \textbf{Discovery} &
    	See OTG-AUTHN-004.
    \\
    \textbf{Likelihood} & 
    	An Atacker can use the informations presented by the error messages to validate further atacks. This results in a higher likelihood for other atacks.
    \\
    \textbf{Impact} & 
    	An atacker can use the application errors to estimate application internas like file and include structures. The knowledge that there is a router involved can lead to specific atacks for routing components.
    \\
    \textbf{Recommen\-dations} &
        Hide the direct errors and transalte them to more general custom error messages.
    \\ \hline
    \textbf{CVSS} &
        \begin{tabular}[t]{@{}l | l}
            Attack Vector           & \textcolor{red}{Network} \\
            Attack Complexity       & \textcolor{red}{Low} \\
            Privileges Required     & \textcolor{red}{None} \\
            User Interaction        & \textcolor{red}{None} \\
            Scope                   & \textcolor{Green}{Unchanged} \\
            Confidentiality Impact  & \textcolor{Green}{None} \\
            Integrity Impact        & \textcolor{Green}{None} \\
            Availability Impact     & \textcolor{Green}{None}
        \end{tabular}
    \\ \hline
\end{longtable}

\subsubsection{Comparison}
BANK-APP does not disclose Stack Traces but SecureBank returns a Stack Trace for unauthorized access.
\clearpage