\section{Session Variables, Fixation and Puzzling}

\subsection{Attack Description}
Session Fixation is an attack that permits an attacker to hijack a valid user session. The attack explores a limitation in the way the web application manages the session ID. When authenticating a user, it doesn’t assign a new session ID, making it possible to use an existent session ID. The attack consists of obtaining a valid session ID, inducing a user to authenticate him/herself with that session ID, and then hijacking the user-validated session by the knowledge of the used session ID. The attacker has to provide a legitimate Web application session ID and try to make the victim's browser use it. \\

This is generally exploitable due to exposed session variables. The session tokens such as Cookie, SessionID, Hidden Field; if exposed, will usually enable an attacker to impersonate a victim and access the application illegitimately. It is important that they are protected from eavesdropping at all times, particularly while in transit between the client browser and the application servers. 

\subsection{Countermeasure}
In order to safeguard the application from vulnerabilities related to Session variables, following measures are undertaken in the \textbf{SecureBank} application.
\begin{itemize}
\item \textbf{Usage of single Session cookie} - By using the same session cookie \textit{PHPSESSID} everywhere in the application, Session overloading is prevented. The session variables are set in the file \textit{SessionService.php} which is invoked once during login.
\item \textbf{Secure Session Cookie}
The session cookie has the \textit{secure} and \textit{httponly} flags set in the file \textit{Service/SessionService.php}. This eliminates the possibility of setting the cookie from client side Javascript or other methods.
\item \textbf{Session Timeout} - The Session is terminated by PHP after the standard value of 1440s
inactivity. This has been implemented in the file \textit{Service/SessionService.php} where no explicit Session timeout is specified.
\end{itemize}

\clearpage