\subsection{Testing for Browser cache weakness - OTG-AUTHN-006}

\subsubsection{Observation}
It is found that sensitive data is not saved anywhere throughout the application. This is achieved with the header \\
\textit{"Cache-Control: must-revalidate, pre-check=0, post-check=0, no-store, no-cache"}. \\
The Back button of the browser neither re-logs the user in nor shows the last opened view.

\subsubsection{Discovery}
This vulnerability was detected using the Burp Suite, About Cache feature of the Firefox browser and manual testing. \\
\\Steps:\\
\underline{\textbf{Detecting cache headers}}\\
\\The response headers were observed through the Burp Suite tool.\\
1. In the browser, under Tools - set the Foxy Proxy Standard to use Burp Suite for all URLs.\\
2. Now open the Burp Suite tool.\\
3. Open the site in the browser and login with credentials.\\
Browser Cache was further inspected with Mozilla's built in tool (about:cache). \\
\\\underline{\textbf{Testing cache weakness}} \\
\\1. Open the application in the browser and login with valid credentials.\\
2. The Transactions page is displayed. Click on the logout button.\\
3. User is redirected to the Login page. Click on the Back button of the browser.\\
There is no redirection to the Transactions page, because of the Cache Control header that states that the cache should be revalidated. Hence user remains on the login page.
\subsubsection{Likelihood}
Likelihood of the vulnerability is low since the attacker needs to change Cache Control header of the application, which requires technical knowledge about analyzing requests and how to modify them.

\subsubsection{Impact}
If the browser caches sensitive data, then it is possible to perform attacks such as session hijacking and Denial of Service.

\subsubsection{CVSS}
\begin{tabular}{l | l}
Attack Vector		& Network \\
Attack Complexity	& High \\
Privileges Required & None \\
User Interaction	& None \\
Scope				& Unchanged \\
Confidentiality		& High \\
Integrity			& None \\
Availability		& None
\end{tabular}

\subsubsection{Comparison with our application}
In our application, a similar header is set for Cache control thereby preventing sensitive data from being saved in the browser cache.

\subsubsection{Recommendation}
NA
\clearpage