\section{External Libraries} \label{section_libraries}

\begin{enumerate}
\item \textbf{Admin LTE} - Admin LTE is a free Bootstrap dashboard theme from \textit{almsaeedstudio}. It is fully responsive and built on top of Bootstrap 3. Typical interface features such as Registration \& Login pages, Dashboard, Navigation components have been incorporated in the banking application.  

\item \textbf{Twitter Bootstrap} - \textit{Bootstrap} is a front-end open-source framework, that contains HTML and CSS-based templates for forms, buttons and other UI components. It aims to ease the development of dynamic websites and web applications. In the application, Bootstrap has been mainly used for styling purposes. Pre-defined styles for various components have been customized accordingly to suit our own requirements.

\item \textbf{jQuery} - \textit{jQuery} is a JavaScript library which is used to simplify the client-side scripting of HTML. The usage in the application is minimal and is limited mainly to customization of properties of the \textit{Data-Table} component and operations related to the \textit{Modal Dialogs}.

\item \textbf{FPDF} - \textit{FPDF} is a PHP class which allows to generate PDF files with pure PHP, that is to say without using the PDFlib library. The generation speed of the document is less than with PDFlib. Most features of the library are utilized effectively, be it for layouting, formatting or for capabilities such as file locking with password. This specific feature has been used to generate the PDF containing the secure TANs for the customer.

\item \textbf{PSR-4 CLassLoader} - This PHP component is provided by \textit{Symfony}. The \textit{ClassLoader} component provides tools to auto-load the classes and cache their locations for performance. Whenever a class that has not been required or included yet; is referenced, PHP uses the auto-loading mechanism to delegate the loading of a file defining the class.

The \textit{PSR-4 Class Loader}  loads classes that follow the PSR-4 class naming standard. 
This PSR describes a specification for auto-loading classes from file paths. It is fully inter-operable, and can be used in addition to any other auto-loading specification, including \textit{PSR-0}. This PSR also describes where to place files that will be auto-loaded according to the specification.

\end{enumerate}

\clearpage