\subsection{Testing for HTTP Verb Tampering - OTG-INPVAL-003}
\subsubsection{BANK-APP}
\begin{longtable}[l]{ p{2.3cm} | p{.79\linewidth} }\hline
    & \textbf{BANK-APP}
    \\ \hline
    \textbf{Observation} &
         It was observed that Verb Tampering could be done with HTTP requests but no critical vulnerability was exposed with it. Methods that were allowed :
           \begin{itemize}
     	      \item  GET
     	      \item  POST
     	      \item  HEAD
     	      \item OPTIONS
           \end{itemize}
           Methods that were rejected:
           \begin{itemize}
       	      \item  TRACE
       	      \item  CONNECT
           \end{itemize}
           With HEAD requests, there were no response data shown. In case of \code{TRACE} and \code{CONNECT}, the requests were rejected because of Same Origin Security restriction.
    \\
    \textbf{Discovery} &
     Advanced Rest Client, an extension for the Google Chrome browser, was used to perform HTTP Verb Tampering.Steps are as follows:
           \begin{itemize}
     	      \item Open the extension in Chrome and enter the URL to be tested.
     	      \item Then one select the type of request (GET, POST, PUT, PATCH, DELETE, HEAD, OPTIONS). Based on the type of HTTP request other details can be filled.
     	      \item Click on the Send button. Response can be seen in the lower section which helps in determining the criticality of the tampering done.
           \end{itemize}
    \\
    \textbf{Likelihood} & N/A \\
    \textbf{Impact} & N/A \\
    \textbf{Recommen\-dations} & N/A \\ \hline
    \textbf{CVSS} & N/A
    \\ \hline
\end{longtable}

\subsubsection{SecureBank}
\begin{longtable}[l]{ p{2.3cm} | p{.79\linewidth} }\hline
    & \textbf{SecureBank}
    \\ \hline
    \textbf{Observation} & It has been observed that Verb Tampering is possible but without any vulnerability being exposed to the attacker.\\
    \textbf{Discovery} & Same as observed for BANK-APP. \\
    \textbf{Likelihood} & N/A \\
    \textbf{Impact} & N/A \\
    \textbf{Recommen\-dations} & N/A\\ \hline
    \textbf{CVSS} & N/A
    \\ \hline
\end{longtable}

\subsubsection{Comparison}
Neither application exposes vulnerability though verb tampering is possible. Hence both seem secure.
\clearpage