\subsection{Testing Directory traversal/file include - OTG-AUTHZ-001}
\subsubsection{InternetBanking}
\begin{longtable}[l]{ p{2.3cm} | p{.79\linewidth} }\hline
    & \textbf{InternetBanking}
    \hfill CVSS Score: 7.5 \progressbar[filledcolor=red]{0.75}
    \\ \hline
    \textbf{Observation} & Generally speaking, files can be downloaded from and directory listing is enable for all folders with three exceptions. Accessing files in the folders \code{controller}, \code{model} and \code{view} shows a blank page. For example you can download the main c-file for the parser via the link \code{http://IP\_ADDRESS/\allowbreak InternetBanking/\allowbreak parser/main.c}. Although the page shows "not permitted", the browser lets the user save the file. \\
    \textbf{Discovery} & In each of the folders \code{controller}, \code{model} and \code{view} there is a \code{index.php} file which simply outputs a blank page. For the other folders you could access the path for the files and download them. \\
    \textbf{Likelihood} & If a hacker knows the folder structure of the application, he/she could easily download all the source code files and look for vulnerabilities. \\
    \textbf{Impact} & Depending on the content of the files a hacker could use that information for attacking the application. \\
    \textbf{Recommen\-dations} & Disable directory listing for hiding sensitive information. \\ \hline
    \textbf{CVSS} &
        \begin{tabular}[t]{@{}l | l}
            Attack Vector           & \textcolor{red}{Network} \\
            Attack Complexity       & \textcolor{red}{Low} \\
            Privileges Required     & \textcolor{red}{None} \\
            User Interaction        & \textcolor{red}{None} \\
            Scope                   & \textcolor{Green}{Unchanged} \\
            Confidentiality Impact  & \textcolor{red}{High} \\
            Integrity Impact        & \textcolor{Green}{None} \\
            Availability Impact     & \textcolor{Green}{None}
        \end{tabular}
    \\ \hline
\end{longtable}

\subsubsection{SecureBank}
\begin{longtable}[l]{ p{2.3cm} | p{.79\linewidth} }\hline
    & \textbf{SecureBank} \\ \hline
    \textbf{Observation} & Directory listing is disabled. \\
    \textbf{Discovery} & In the \code{src/.htaccess} file there is the line with \code{Options -Indexes}, which disables directory listing. \\
    \textbf{Likelihood} & N/A \\
    \textbf{Impact} & N/A \\
    \textbf{Recommen\-dations} & N/A \\ \hline
    \textbf{CVSS} & N/A \\ \hline
\end{longtable}

\subsubsection{Comparison}
InternetBanking has directory listing for some folders enabled, whereas SecureBank does not. Therefore it is possible to download some source code from InternetBanking by directly accessing the files/folders.

\clearpage